Handbook streamFind: Backend

### 2023-03-06 README.Rmd
Continuation of R6 implementation 28
Updated README and logos moved to man/figures/

The R package `streamFind` (this repository) is the back-end platform for the streamFind project entitled "Flexible data analysis and workflow designer to identify chemicals in the water cycle". The streamFind project is funded by the [Bundesministerium für Bildung und Forschung (BMBF)](https://www.bmbf.de) and is a cooperation between the [Institut für Energie- und Umwelttechnik e. V. (IUTA)](https://www.iuta.de) and [Forschungszentrum Informatik (FZI)](https://www.fzi.de/). The major focus of `streamFind` is data processing for environmental and quality studies. The `streamFind` R aims to stimulate the use of advanced data analysis (e.g., non-target screening, statistical analysis, etc.) in routine studies, promoting standardization of data processing and structure and easing the retrospective evaluation of data. The streamFind package can be used by academics but also by technicians due to the comprehensive documentation and well categorized set of integrated functions or modules (see vignettes for more information).

```{r, echo=FALSE, out.width = '100%', fig.align='center'}
knitr::include_graphics("inst/extdata/logo_group.png")
```

@@

For installation of the `streamFind` R package, it is recommended to firstly ensure that the dependencies are currently installed. Several existing R packages and external software are used in `streamFind` for various processing steps. A major dependency of `streamFind` is the [patRoon](https://github.com/rickhelmus/patRoon) R package. The `patRoon` R package combines several tools for basic and advanced data processing and can be used interchangeably with `streamFind`.

@@

#### R and RTools

@@

#### patRoon

@@

The [streamFind](https://github.com/ricardobachertdacunha/streamFind) R package can be installed from the GitHub repository with the following code line:

@@

## Docker image

Not yet available.

## Backend usage

Consult the Handbook_backend_streamFind.Rmd in the handbooks folder for detailed back-end structure and usage documentation.

>>>>

The R package [streamFind](https://github.com/ricardobachertdacunha/streamFind) (this repository) is the back-end platform for the streamFind project entitled "Flexible data analysis and workflow designer to identify chemicals in the water cycle". The streamFind project is funded by the [Bundesministerium für Bildung und Forschung (BMBF)](https://www.bmbf.de) and is a cooperation between the [Institut für Energie- und Umwelttechnik e. V. (IUTA)](https://www.iuta.de) and [Forschungszentrum Informatik (FZI)](https://www.fzi.de/). The major focus of streamFind is data processing for environmental and quality studies. The streamFind aims to stimulate the use of advanced data analysis (e.g., non-target screening, statistical analysis, etc.) in routine studies, promoting standardization of data processing and structure and easing the retrospective evaluation of data. The streamFind package can be used by academics but also by technicians due to the comprehensive documentation and well categorized set of integrated functions or modules (see vignettes for more information).

```{r, echo=FALSE, out.width = '100%', fig.align='center'}
knitr::include_graphics("man/figures/logo_group.png")
```

@@

For installation of the [streamFind](https://github.com/ricardobachertdacunha/streamFind) R package, it is recommended to firstly ensure that the dependencies are currently installed. Several existing R packages and external software are used in streamFind for various processing steps. A major dependency of streamFind is the [patRoon](https://github.com/rickhelmus/patRoon) R package. The [patRoon](https://github.com/rickhelmus/patRoon) R package combines several tools for basic and advanced data processing and can be used interchangeably with streamFind.

@@

@@

@@

The [streamFind](https://github.com/ricardobachertdacunha/streamFind) R package can be installed from the GitHub repository with the following code line.

@@

The [streamFindData](https://github.com/ricardobachertdacunha/streamFindData) R package holds the data used in examples and other documentation assets of the streamFind R package and can be installed from the GitHub repository with the following code line.

```{r install-streamfinddata, eval=FALSE}
remotes::install_github("ricardobachertdacunha/streamFindData")
```
